%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%packages
\documentclass[8pt]{resume}
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
%\usepackage{wasysym}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage[misc]{ifsym}
%document margins
\usepackage[left=1.4cm,top=0.3in,right=1.6cm,bottom=0.5in]{geometry}

%macros
\newcommand{\tit}[1]{\textit{#1}}
\newcommand{\tbf}[1]{\textbf{#1}}
\newcommand{\ttt}[1]{\texttt{#1}}

%doc begin
\name{Erik de Godoy Perillo}
%\address{Rua Paulinia, 396 \\ Americana, SP -- Brazil}
\address{Americana, SP -- Brazil}
\address{\faMobilePhone~+55 31 973248225
   ~~\Letter~erik.perillo@gmail.com
   ~~$\triangleright$~erikperillo.xyz}

\begin{document}

\begin{rSection}{Experience}

\begin{rSubsection}{Agronow}{2018 - Present}{Machine Learning Engineer}
    {São Paulo, Brazil}
    \item Developed Machine Learning solutions for agriculture, implementing services such as identification of crops (soybean, sugarcane, corn)
        with Tensorflow on ESA Sentinel-2 satellite imagery.
\end{rSubsection}

\begin{rSubsection}{Google}{2017 - 2018}{Software Engineering Intern}
    {Belo Horizonte, Brazil}
    \item Worked on the sports experience in search, successfully developing and launching features to production.
    \item Developed a UI change in the sports onebox using Java/Javascript/CSS/HTML and other technologies.
\end{rSubsection}

\begin{rSubsection}{GAIIA tech (startup)}{2017 - 2017}{Chief Technology Officer}
    {São Paulo, Brazil}
    \item Built Deep Learning models that allowed identification of crops in brazilian farms using satellite imagery.
    \item Leader of the development team, providing insights to
        those involved in 2017 soybean season in Brazil.
\end{rSubsection}

%\begin{rSubsection}{Phoenix Team of Robotics}{2013 - 2016}{Project Manager}{University of Campinas, Brazil}
\begin{rSubsection}{Phoenix Robotics Team - Unicamp}{2013 - 2016}{Project Manager}
    {Campinas, Brazil}
    %\item Led two successful teams with around 6 people each.
\item Leader of projects \tit{Piranha}/\tit{Baleia},
        two autonomous mini-vehicles (5-7 people team).
        Third/First place in \tit{Robocore}'s latin-american 2015/2016 robotics
        challenge, setting a new record.
    \item Built navigation, communication and computer vision systems
        during the conception of 3 autonomous robots using technologies such as PID control, C++, Python, CUDA OpenCV, NXP/Jetson TX1 platforms.
\end{rSubsection}

%\begin{rSubsection}{Institute of Computing}{2016 - Present}{Undergraduate Researcher on Artificial Intelligence (grant by CNPQ)}
\begin{rSubsection}{Institute of Computing - Unicamp}{2016 - 2017}{Undergraduate Researcher on Artificial Intelligence}
    {Campinas, Brazil}
    %\item Working towards a framework for real-time vision
    %    allowing mobile robots to explore a variety of environments.
    \item Created a visual saliency detection system using Deep Learning (Theano/Tensorflow).
        Our model has around 3/4 less parameters than similar methods yet
        achieves top-10 performance on MIT300 benchmark.
    \item Best Undergraduate Research Project Award on WTD2017 conference at
        Unicamp.
        %Our preliminary results from MIT300 benchmark suggest performance
        %close to other models with similar architecture.
    %\item I am currently implementing state-of-the-art techniques for
    %    saliency detection using deep learning.
\end{rSubsection}

%\begin{rSubsection}{Undergraduate Researcher on High Performance Computing}{2014 - 2015}{Computational Mechanics Laboratory, University of Campinas}{Campinas, Brazil}
%    \item Designed a tool using Machine Learning to infer performance
%        in ccNUMA systems, saving $66\%$ of the time to
%        determine the best memory policy for applications.
%    \item Our work resulted in a paper accepted for ERAD-SP 2017 conference in Brazil.
%\end{rSubsection}

%\begin{rSubsection}{Undergraduate Researcher on Computer Vision}{2013 - 2014}{Renato Archer Center of Technology}{Campinas, Brazil}
%    \item Built a tool for real-time indoors tracking of
%        mobile robots using OpenCV (C++),
%        achieving tracking of more objects compared to the older system
%        and no need for special hardware (only webcams).
%\end{rSubsection}

\end{rSection}

\begin{rSection}{Education}
    \begin{rSubsection}{Masters in Artificial Intelligence}{2018 - Present}{University of Campinas (Unicamp)}{Campinas, Brazil}
    \item Ranked first place in the admission process.

    \begin{rSubsection}{B.S. in Computer Science}{2015 - 2018}{University of Campinas (Unicamp)}{Campinas, Brazil}
    \item Teaching Assistant (2016/2017) in \tit{Data Structures}. Helped
        design/administer programming assignments.
    \item Last GPA: 8.8/10 (first in class).
    %\item Coursework in Control Engineering (2012-2014) including:
    %    Dynamics, Statics, Linear Systems.
    %\item Unicamp is ranked second best
    %    (overall and in Computer Science) in latin america according to
    %    QS rankings 2016.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Projects}
\begin{rSubsection}{}{}{}{}
    \vspace{-0.5em}
    \item \tbf{\ttt{golb}}: Minimalistic blog platform built with Django.
    %\item \tbf{\ttt{Piranha Robot}}:
    %    built inter-communication system using UDP protocol (C++),
    %    vision system using CUDA OpenCV (C++/Python),
    %    helped build PID control unit using NXP platform/sensors (C/C++).
    %\item \tbf{\ttt{hct}}: Real time hashtag counter using Twitter Streaming API and
    %    Apache Spark.
    %\item \tbf{\ttt{Baleia Robot}}:
    %    built navigation system with Adafruit's BBIO library and
    %    vision system with OpenCV.
    %\item \tbf{\ttt{oarg}}: A command-line argument parser for Python.
    \item \tbf{\ttt{ichat}}: TCP command-line chat in C++ with file transfer and
        notifications.
    %\item \ttt{imsg}: Steganography for images written in Python.
    %\item \ttt{mlct}: Naive Bayes text classifier for big volumes of data using
    %    Apache Spark Mlib.
    %\item \ttt{findr}: Object finder using image classifier with OpenCV in
    %    Python/C++.
\end{rSubsection}

\end{rSection}

\end{document}
